---
title: "Untitled"
author: "John Tarr"
date: "October 30, 2015"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    includes:
      in_header: ../TEX/header.tex
  html_document:
    highlight: kate
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  word_document: default
---

\markasdraft

```{r comments_chunk, include=FALSE}
# ------------------------------------------------------------------------------
# *** Basic Info - This section only needed in R scripts
# Name: See documentation for package, see YAML for RMD
# Developer: See documentation for package, see YAML for RMD
# Date: See documentation for package, see YAML for RMD
# Purpose: See documentation for package, see Markdown for RMD
# ------------------------------------------------------------------------------
# *** Project Folder Structure
# Code
#   - R -> Any R or RMD files
#   - SQL -> SQL scripts to be read by R and executed against DB
#         -> Cleaner than having the SQL directly in the R file
#   - TEX -> A header.tex file that is explained further below
# Data
#   - Originals -> The original version, should be read only
#   - HandModified -> If I have to create data by hand or modify an original
#   - PreProcessed -> If processing the data takes significant time
#                  -> Also useful if pre-processing is done by an outside program
# Output
#   - This folder should be entirely reproducable from the R script
#   - Only exception is the PDF file. Need to learn how to override KnitPDF button
#   - All spreadsheet, plot, etc output should go here
#   - If I have manually collected data, use R to copy from Data to Output
# Project Documentation
#   - Supporting documentation
# ------------------------------------------------------------------------------
# *** YAML Comments
# I typically output to PDF with a 3 layer table of contents
# The HTML and Word would probably need some adjusting if I started using them
# Note header.tex, which allows me to perform the following functions:
#     - \newpage -> Creates a page break, as you'd expect
#     - \blandscape -> Begins landscape mode and rotates the page
#                   -> Must have matching elandscape for blandscape
#                   -> Don't forget to alter figwidth/figheight on landscape chunks
#                   -> Not doing so can result in a leading blank page
#     - \elandscape -> Ends landscape and goes back to portrait
#     - \markasdraft -> Prints draft diagonally across the page
# ------------------------------------------------------------------------------
# *** Change Log
# ******
# YYYY/MM/DD - JNT  - Changed ABC because XYZ
#                   - This is a second line if needed
# ******
# YYYY/MM/DD - JNT  - Changed ABC because XYZ
#                   - This is a second line if needed
# ******
# ------------------------------------------------------------------------------
# *** To do items
# JNT - Need to check for condition where XYZ
# JNT - Turn repeated data frame clean up into function
#     - When making function, don't forget to...
# ------------------------------------------------------------------------------
```

```{r libraries_chunk, include=FALSE}
# ------------------------------------------------------------------------------
# *** Packages Chunk
# This is just a chunk to load all packages used in the project
# include=FALSE keeps this code, results, errors, etc from displaying
# ------------------------------------------------------------------------------

# *** Ingestion
library(RODBC)
library(readxl)
library(readr)

# *** Manipulation
library('data.table')
library(dplyr)
library(tidyr)
library(magrittr)
library(descr)
library(questionr)
library(lubridate)

# *** Visualization
#library(ggvis) # HTML and interactive plots
library(ggplot2)
library(scales)
library(gridExtra)
library(gclus) # For histograms with correlation color coding
library(GGally) # Installed for ggpairs, upgraded pairs function

# *** Presentation
library(knitr)

# *** Personal Packages
library(mahPackage)
```

```{r knitr_setup_chunk, include=FALSE}
# ------------------------------------------------------------------------------
# *** knitr Setup Chunk
# This is a way to set options for all code chunks at once
# After this, we don't need include=FALSE, as we want the output to display
# Also sets the working directory for knitr
# ------------------------------------------------------------------------------
# *** Possible enhancements if needed
# You can set options to a variable instead of hardcoding
# A possible use might be a "developer mode" and a "publication mode"
# One would echo code, and the other would not, for instance

# You can also control options by output type, as with the code below:
# output <- opts_knit$get("rmarkdown.pandoc.to") # "html", "latex", "docx"
# if (output=="latex") opts_chunk$set(fig.width=11, fig.height=11)
# ------------------------------------------------------------------------------

# *** Chunk Options
knitr::opts_chunk$set(echo=FALSE,     # My customers won't want to see code
                      warning=FALSE,  # Same for warning messages, I can catch them in the console
                      message=FALSE,  # Same for messages
                      include=TRUE,   # Include defaults to true, shows code results
                      fig.width = 10, # Experimented with this
                      fig.height = 7, # Same as above
                      dev="png",      # Not sure why, copied this
                      dpi=200,        # Was getting poor image quality, increased DPI
                      dev.args=list(type="cairo")) # cairo used for anti-aliasing

# *** Working Directory
# RStudio uses the project folder as the working directory
# knitr uses the location of the .RMD file as the working directory
# This moves knitr's WD up to RStudio's WD
knitr::opts_knit$set(root.dir = "../../")
```

```{r r_setup_chunk}
# ------------------------------------------------------------------------------
# *** Setup Chunk
# Some basic things to set up for the script
# ------------------------------------------------------------------------------

# Clears the environment
# Stale variables can mask issues when testing
rm(list = ls())

# Turns off scientific notation
# My customers prefer standard decimal
options(scipen = 999)

# By default, R will try to factor strings it reads in
# Manipulating the strings is easier, can always factor later
options(stringsAsFactors = FALSE)
```

```{r read_spreadsheets_chunk}
# ------------------------------------------------------------------------------
# *** Read Spreadsheets Chunk
# read_excel uses readXL, pretty basic, can exclude col_types
# ------------------------------------------------------------------------------

# *** myFile.xlsx
# Source: 
# Date: 
# Details: 

myDataFrame <- read_excel("Data/Originals/myFile.xlsx", 
                      sheet = "Sheet1", 
                      col_types = c("numeric", "text", "date"))
```

```{r read_database_chunk}
# ------------------------------------------------------------------------------
# *** Read Database Chunk
# Two connections listed below, one for DEV and one for PRD
# The base SQL file is read in from the Code/SQL folder and modified
# ------------------------------------------------------------------------------

# *** SQL Connection
# DEV
#SQLServer <- odbcDriverConnect(connection = "Driver={SQL Server};server=<<server>>;database=<<db>>;trusted_connection=yes")
# PRD
#SQLServer <- odbcDriverConnect(connection = "Driver={SQL Server};server=<<server>>;database=<<db>>;trusted_connection=yes")

# *** SQL Query - <<name>>
#sqlTextFile <- read_file("Code/SQL/<<file>>.sql")
#sqlStatement <- sqlTextFile
#sqlStatement <- gsub("@start_date", '2027-01-01', sqlStatement)
#sqlStatement <- gsub("@end_date", '2027-01-01', sqlStatement)
#sqlResult <- sqlQuery(SQLServer, sqlStatement)
```

\newpage

# Abstract

Executive summary of all other sections.

# Introduction

## Purpose

Why you're doing the analysis.

## Background Info

Information about the processes you're investigating.

# Methods

## Data Acquisition

Where you got the data, report names, person, system, etc.

## Sanity Checks

What did you do to ensure the data is valid?

## Data Cleanup

What did you remove/alter to clean the data for analysis?

## Data Analysis

The actual analysis.

# Results

Summary of what you found.

# Conclusions

The conclusions you feel you can draw from your results.

```{r copy_raw_files_chunk}
# ------------------------------------------------------------------------------
# *** Copy Raw Files Chunk
# Very basic code to copy any files directly to output.
# If you generated data outside of R, or wanted to copy the original files.
# ------------------------------------------------------------------------------

#file.copy('Data/Originals/myFile.xlsx', 'Output/myFile.xlsx', overwrite = TRUE, recursive = FALSE,
#          copy.mode = TRUE, copy.date = TRUE)
```
